Internal Gravity Wave Breaking in White Dwarf Binaries

### 2019-10-09 writeups/Su_IGW_break.tex
stash

To solve for the excited wave amplitude in the linear problem, consider the
complexified linearized system of equations, then $\pd{}{t} \to -i\omega,
\pd{}{x} \to ik_x$. This gives (extracting the $e^{ik_xx - i\omega t}$ mode)
\begin{align*}
    \pd{u_{z}'}{z} + ik_xu_x' &= 0,\\
    -i\omega u_x' + ik_x \varpi' + gHik_x \Upsilon &= 0,\\
    -i\omega u_{z}' + \pd{\varpi'}{z} + gH\pd{\Upsilon}{z}
        - \frac{\varpi'}{H} &= 0,\\
    -i\omega \Upsilon - \frac{u_{z}'}{H} &=
        Ce^{-\frac{(z - z_0)^2}{2\sigma^2}}.
\end{align*}
Compare to the left hand side of \autoref{se:dedalus_eqs} below. This can be
recast solely in terms of
$u_{1z}$ as
\begin{align*}
    \omega^2\p{
        k_x^2u_{z}' + \frac{1}{H}\pd{u_{z}'}{z} - \ptd{u_{z}'}{z}
    } - u_{z}'N^2k_x^2 =
    gk_x^2Ce^{-\frac{(z - z_0)^2}{2\sigma^2}}.
\end{align*}
% In the limit $\sigma \to 0$, the right hand side can be approximated
% $e^{-\frac{(z - z_0)^2}{2\sigma^2}} \approx \sigma\sqrt{2\pi}\delta\p{z - z_0}$.
% Matching this against a singularity in $\ptd{u_z'}{z}$, or a kick in
% $\pd{u_z'}{z}$, gives \autoref{eq:uz_lin}.
The homogeneous solutions are

>>>>

To solve for the excited wave amplitude in the linear problem, consider the
complexified linearized system of equations, then $\pd{}{t} \to -i\omega,
\pd{}{x} \to ik_x$. Assuming all fields have dependence $u_z(x, z, t) = u_z'(z)
e^{ik_xx - i\omega t}$, this gives:
\begin{align*}
    \rd{u_{z}'}{z} + ik_xu_x' &= 0,\\
    -i\omega u_x' + ik_x \varpi' + gHik_x \Upsilon &= 0,\\
    -i\omega u_{z}' + \rd{\varpi'}{z} + gH\rd{\Upsilon}{z}
        - \frac{\varpi'}{H} &= 0,\\
    -i\omega \Upsilon - \frac{u_{z}'}{H} &=
        Ce^{-\frac{(z - z_0)^2}{2\sigma^2}}.
\end{align*}
We have replaced all partial derivatives with regular derivatives. Compare to
the left hand side of \autoref{se:dedalus_eqs} below. This can be recast solely
in terms of $u_{1z}$ as
\begin{align*}
    \omega^2\p{
        k_x^2u_{z}' + \frac{1}{H}\rd{u_{z}'}{z} - \rtd{u_{z}'}{z}
    } - u_{z}'N^2k_x^2 =
    gk_x^2Ce^{-\frac{(z - z_0)^2}{2\sigma^2}}.
\end{align*}
% In the limit $\sigma \to 0$, the right hand side can be approximated
% $e^{-\frac{(z - z_0)^2}{2\sigma^2}} \approx \sigma\sqrt{2\pi}\delta\p{z - z_0}$.
% Matching this against a singularity in $\ptd{u_z'}{z}$, or a kick in
% $\pd{u_z'}{z}$, gives \autoref{eq:uz_lin}.
We compute the solution to the inhomogeneous ODE by the method of variation of
parameters. The homogeneous solutions are of form $u_{z,\pm}'(z) =
e^{\frac{z}{2H} \pm ik_zz}$ where $k_z$ satisfies the dispersion relation
\autoref{eq:disp_rel}. The Wronskian can be computed
\begin{equation}
    W \equiv \det \begin{vmatrix}
        u_{z,+}' & u_{z,-}' \\[4pt]
        \rd{u_{z,+}'}{z} & \rd{u_{z,-}'}{z}
    \end{vmatrix} = -2ik_ze^{z/H}.
\end{equation}
